Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-28 cav2017/cav2017.tex
wording

We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
number $x$ represented in the fixed-point precision level of the controller,
and $\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
represented in the fixed-point precision level of the plant computational
model ($I_p \geq I_c \wedge\allowbreak F_p \geq F_c$).  Thus any mathematical
operations occurring in the digital controller will occur in the range of
$\mathcal{F}_{\langle I_c,F_c \rangle}$, and all other calculations will be
carried out in the range of $\mathcal{F}_{\langle I_p,F_p \rangle}$.  The
physical plant operates in the reals, which means our verification phase
must account for calculation errors in the model.

>>>>

We will use $\mathcal{F}_{\langle I_c,F_c \rangle}(x)$ to denote a real
number $x$ represented at the fixed-point precision of the controller, and
$\mathcal{F}_{\langle I_p,F_p \rangle}(x)$ to denote a real number $x$
represented at the fixed-point precision of the plant model ($I_p \geq I_c
\wedge\allowbreak F_p \geq F_c$).  Thus any mathematical operations in the
digital controller will be in the range of $\mathcal{F}_{\langle I_c,F_c
\rangle}$, and all other calculations will be carried out in the range of
$\mathcal{F}_{\langle I_p,F_p \rangle}$.  The physical plant operates in the
reals, which means our verification phase must account for calculation
errors in the model.
